Token-level author diarization using clustering of stylistic contexts

### 2017-06-02 paper/paper.tex
Added some text to the cocnlusion

We have evaluated our models using micro-averaged and macro-averaged precision, recall and $F_1$-score for intrinsic plagiarism detection and the analogous BCubed scores for author diarization, as defined in subsection \ref{subsec:evaluation-measures}. The results of our models are compared to the reuslts of our baselines, a well as the results of the two teams that took part in the PAN 2016 competition for this problem. The results of the two teams have been evaluated on test sets that is not publicly available. Only the training sets from the competition have been available to us.

@@

Our results, as well as the the results of others, suggest that author diarization and intrinsic plagiarism detection are challenging problems. Our approach

@@

% 2-nd paragraph further work
% more systematic parameter choice, model development
% mention possible applicability to author clustering and extrinsic plagiarism detections

>>>>

We have evaluated our models using micro-averaged and macro-averaged precision, recall and $F_1$-score for intrinsic plagiarism detection and the analogous BCubed scores for author diarization, as defined in subsection \ref{subsec:evaluation-measures}. The results of our models are compared to the results of our baselines, a well as the results of the two teams that took part in the PAN 2016 competition for this problem. The results of the two teams have been evaluated on test sets that is not publicly available. Only the training sets from the competition have been available to us.

@@

Our results, as well as the the results of others, suggest that author diarization and intrinsic plagiarism detection are very challenging problems. Our approach tries to solve the problem by clustering contextual writing style features extracted with a sliding window around each token.

We have presented some ideas that are not completely refined but, based on the data we have available, seem to give comparable, or even better results that the other two approaches that tired to tackle the same problem.

@@

% 2-nd paragraph further work
% basic feature extraction speed sliding window overlap?
% more systematic parameter choice, further model development
% mention possible applicability to author clustering and extrinsic plagiarism detections
